---
title: "Analyse diamonds data with ggplot"
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r}
library(dplyr)
library(tidyverse)
library(patchwork)
library(RColorBrewer)
```

## Data Information

```{r}
glimpse(diamonds)

```

## plot cut vs color

```{r}
ggplot(diamonds, aes(cut, 
                     fill=color)) +
  geom_bar(position = "dodge")

```

## Relationship between price and color of diamonds with boxplot

```{r}
ggplot(diamonds, aes(price, color)) +
geom_boxplot() +
labs(
title = "Relationship between price and color of diamonds",
x = "price",
y = "color",
subtitle = "Using ggplot to create this visualization",
caption = "Source: ggplot package"
) +
stat_summary(color = "#993404")+
stat_summary(
fun.min = function(x) mean(x) - sd(x)
,fun.max = function(x) mean(x) + sd(x)
,geom = "errorbar"
,color = "#993404"
,width = 0.5
) +
theme_minimal()
```

We find that color j has the highest average price and the color j diamonds have the largest interquartile range and they have a median of around 4700, which is the highest. On the other hand, the color j diamonds have the lowest median, which is a have a median of around 3000

## The relationship between table and the average price of diamonds separated, by cut

```{r}
df %>% group_by(table, cut) %>%
 summarise(avg_p = mean(price)) %>%
 ggplot(aes(table, avg_p, group = cut, color = cut)) +
 geom_point()+
 geom_line()+
 theme_dark()+
 facet_wrap(~ cut, ncol = 4)+
 labs(title = "The relationship between table and the average price of diamonds separated, by cut ",
  x = "Table",
  y = "Average price(USD)",
  caption = "Source: Diamonds from ggplots2 package")+
 scale_color_brewer(type = "seq", palette = "Blues")

```

It can be noted that at the Good and Premium trades, there will be a lower price fluctuation than the rest. Another thing to notice is that the size of the table doesn't affect the price.

## Graph 2. The relationship between clarity and the average price of diamonds seperated by cut.

```{r}
df %>% group_by(clarity, cut) %>%
  summarise(avg_p = mean(price)) %>%
  ggplot(aes(clarity,avg_p, group = cut, color = cut))+
  geom_point()+
  geom_line()+
  theme_minimal()+
    labs(title = "The relationship between clarity and the average price of diamonds seperated by cut",
      x = "clarity",
      y = "Average price (USD)",
      caption = "Source: Diamonds from ggplots2 package")+
  scale_color_brewer(type = "seq", palette = "PuBu")

```

From the graph we can see that clarity with si2 has the highest average price and clarity with VVS1 has the lowest average price.

## Sample plots of carat vs price and trend line group by color

```{r}
df %>%
ggplot(aes(carat, price, color=color)) +

geom_smooth(method="lm", se=F)+
theme_minimal()+
scale_color_brewer(type="qual",palette = "Set2")
```

From the graph where carat is equal to 3, the colors that get the average price from high to low can be g , e , i, h, j.
